The Anatomy of a Temporal Summarization System

### 2015-01-13 paper.tex
formatting and latex errors; added sig-alt
refactoring sections.

%\documentclass{sig-alternate} \usepackage{url} \usepackage{color}
\documentclass[10pt]{article} \usepackage{url} \usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[]{algorithm2e}
\DeclareMathOperator{\corpus}{\mathcal{C}}
\DeclareMathOperator{\doc}{\mathnormal{d}}
\DeclareMathOperator{\sent}{\mathnormal{s}}
\DeclareMathOperator{\order}{\pi}
\DeclareMathOperator{\dtime}{\mathnormal{t}}
\DeclareMathOperator{\hour}{\mathnormal{h}}
\DeclareMathOperator{\hours}{\mathcal{H}}
\DeclareMathOperator{\Sim}{\mathbf{K}}
\DeclareMathOperator{\SMat}{\mathbf{X}}
\DeclareMathOperator{\Pref}{\boldsymbol{\pi}}
\DeclareMathOperator{\Exemp}{\mathnormal{Exemplars}}
\DeclareMathOperator{\Updates}{\mathnormal{Updates}}
\usepackage{cleveref}
\crefname{section}{§}{§§}
\Crefname{section}{§}{§§}

@@

\title{Columbia University at TREC 2014: Temporal Summarization}

\author[1]{Chris Kedzie}
\author[1]{Kathleen McKeown}
\author[2]{Fernando Diaz}
\affil[1]{Columbia University, Department of Computer Science}
\affil[2]{Microsoft Research}
%    Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
%Format\titlenote{(Produces the permission block, and copyright information).
%For use with SIG-ALTERNATE.CLS. Supported by ACM.}} \subtitle{[Extended
%Abstract] \titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement and
% alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time' i.e. three
% 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of "name/affiliations" may
% appear. We just ask that you restrict the number of 'columns' to three.
%
% Because of the available 'opening page real-estate' we ask you to refrain
% from putting more than six authors (two rows with three columns) beneath the
% article title.  More than six makes the first-page appear very cluttered
% indeed.
%
% Use the \alignauthor commands to handle the names and affiliations for an
% 'aesthetic maximum' of six authors.  Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the \additionalauthors
% command.  These 'additional authors' will be output/set for you without
% further effort on your part as the last section in the body of your article
% BEFORE References or any Appendices.

@@

\section{Introduction}

During crises, information is critical for first responders and those caught
in the event.  When the event is significant, as in the case of Hurricane
Sandy, the amount of information produced by traditional news outlets,
government agencies, relief organizations, and social media can vastly
overwhelm those trying to monitor the situation. Methods for identifying,
tracking, and summarizing events from text based input have been explored
extensively  (e.g.,
\cite{allan1998topic,Filatova&Hatzivassiloglou.04a,Wang&al.11}). However,
these experiments were not performed in the large and heterogeneous
environment of the modern web; there is still a need for robust and scalable 
methods for automatic summarization.

%Previous work on generating event descriptions and/or multi-document
%summarization has relied on clustering algorithms to find representative
%sentences appropriate for an event summary.  These methods impose a metric
%space on the text data that can make it difficult to incorporate external
%sources of information elegantly -- in this paper we argue that centroid
%sentences are not a priori the best candidates for inclusion in an event
%summary.

In this paper, we detail our participation in the second year of the TREC
Temporal Summarization (TS) track. Broadly, TS systems are required to monitor
a time ordered corpus for information about a specific event and ``emit'' 
updates about that event. Under the current TREC formulation of this task,
successful TS systems must synthesize techniques from information retrieval,
 extractive multi-document summarization, and update summarization.
Specifically, we must select updates to emit based on three primary criterion:
relevance, salience, and redundancy.

As this was our first time participating in TS track, we focused mostly on 
second and third criterion, relying on the TREC supplied resources for 
document retrieval and filtering heuristics for relevance.
Our system predicts sentence salience in the context of a
large-scale event and integrates these predictions into
a clustering based multi-document summarization system. We fit a Gaussian 
Process (GP) regression model to predict sentence salience and use 
these predictions to bias the
formation of sentence clusters around more salient regions in the input space
using affinity propagation (AP) clustering.  AP uses the salience predictions
as well as pairwise similarities among input sentences to identify
\emph{exemplar} sentences, which we use as our summary output.  Our approach
differs from other methods of summarization that compute salience by pairwise
comparisons alone, ignoring features of importance that are intrinsic to the
sentences themselves.

The remainder of the paper is organized as follows. In section
~\ref{sec:background} we give an overview of the semantic similarity, 
Gaussian process, and affinity propagation algorithms that make up the bulk of
our TS system. 
Next we describe the data with which we build our various models.
Then in section~\ref{sec:approach} we give a high level sketch
of our system, and then explain each component in detail. 
We finish with the presentation of our results and related works.

@@

\begin{figure}
\begin{tabular}{| p{5cm} c c |}
\hline
Event & WP Categories & No. Docs/Sents/Words\\
\hline \hline
Boston\_Marathon\_bombings \newline
Christopher\_Dorner\_shootings\_and\_manhunt \newline 
 In\_Amenas\_hostage\_crisis
& Terrorism, Mass Shootings & 33,732/1,139,588/26,201,659  \\
\hline
 Cyclone\_Oswald \newline
Early\_2012\_European\_cold\_wave \newline
February\_2013\_noreaster \newline & Weather events & 35,554/591,850/12,794,438  \\
\hline
Costa\_Concordia\_disaster & Accidents & 22,874/732,945/16,520,242 \\
\hline
Chelyabinsk\_meteor & Earthquakes & 14,515/283,509/6,135,803  \\
\hline
Port\_Said\_Stadium\_riot \newline
2012\_Afghanistan\_Quran\_burning\_protests \newline
2011-13\_Russian\_protests \newline
2012\_Romanian\_protests \newline
2012-13\_Egyptian\_protests \newline
2013\_Bulgarian\_protests\_against\_the\_Borisov\_cabinet \newline
2013\_Shahbag\_protests & Activism\_by\_type & 464,657/11,254,122/250,172,896  \\
\hline
\end{tabular}
\caption{Domain specific Wikipedia corpora for semantic similarity and 
language models. }
\end{figure}

@@

\begin{figure}
\centering
\begin{algorithm}[H]
 \KwData{$Query$ --- the set of event query words\\ 
        $SC$ --- the stream corpus\\

@@

 } 
 \caption{Temporal Summarization Algorithm}
\end{algorithm}
\end{figure}

@@

\section{Related Work}

A principal concern in extractive multi-document summarization is the
selection of salient sentences for inclusion in summary output
\cite{nenkova2012survey}.  This has often been approached as a ranking
problem.
%We broadly conceptualize this decision as either an intrinsic or extrinsic
%sentence evaluation process. Intrinsic approaches evaluate sentences
%individually, possibly by predicting the impact on summary quality using
%sentece level features. 
Sentences have been ranked by the average word probability, average tf-idf
score, and the number of topically related words (topic-signatures in the
summarization literature)
\cite{nenkova2005impact,hovy1998automated,lin2000automated}. The first two
statistics are easily computable from the input sentences, while the third
only requires an additional, generic background corpus.  Another ranking
approach, centroid summarization, involves creating an average bag of words
(BOW) vector, the centroid, from the input sentences and ranking sentences by
their similarity to the centroid \cite{radev2004centroid}.  Graph
\cite{erkan2004lexrank} and clustering
\cite{hatzivassiloglou2001simfinder,mckeown1999towards,siddharthan2004syntactic}
based approaches, on the other hand, make use of pair-wise similarity
comparisons amongst input sentences.  In these models, salient sentences are
more central to the input or cluster, respectively.

%identify salient regions of the input space while simultaneously coping with
%redundancy.  Graph-based algorithms have been used to rank sentences
%Clustering algorithms, e.g., are commonly used to exploit redundancy in
%input. Input sentences are clustered and summaries are generated by selecting
%the most representative sentence from each cluster.  Graph-based models have
%also been used for summarization.  E.g., the LexRank algorithm treats
%sentences as nodes in a graph, where edges are constructed by way of cosine
%similarity between sentence nodes; edges are either continuosly weighted by
%similarity or discrete, existing only when the similarity is above a
%threshold.  The PageRank algorithm is used on the graph to find the most
%important sentence nodes. In both clustering and graph-based approaches,
%sentence salience is largely determined by the pairwise relations between
%sentences.

Supervised learning has also been applied to this task. Model features are
usually derived from human generated summaries, and are non-lexical in nature
(e.g., sentence starting position, number of topic-signatures, number of
unique words, word frequencies). Seminal work in this area has employed naive
Bayes and logistic regression classifiers to identify sentences for summary
inclusion \cite{kupiec1995trainable,conroy2001using}.

%\fdadd{
Several researchers have recognized the importance of summarization during
natural disasters.  Guo \textit{et al.} developed a system for detecting
novel, relevant, and comprehensive sentences immediately after a natural
disaster \cite{qi:temporal-summarization}.  The method uses a model of
sentence relevance and novelty in order to select appropriate updates.
Training data for regression targets is automatically generated from
retrospective Wikipedia data.  The system is evaluated on news documents
related to 197 natural and human disasters from 2009 to 2011 using variants of
Rouge modified to capture novelty, relevance, and comprehensiveness
\cite{lin2004rouge}.  Wang and Li present a clustering-based approach to
efficiency detect important updates during natural disasters
\cite{wang:update-summarization}.  The algorithm works by hierarchically
clustering sentences online, allowing the system to output a more expressive
narrative structure than Guo \textit{et al.}.  The method is evaluated on
official press releases related to Hurricane Wilma  in 2005 using Rouge score
between the system summary and a manually generated target summary.
%}

%This work uses the TREC Stream Corpus data set that is in use by the TREC
%Temporal Summarization track \cite{frank2012building,aslam2013trec} .
%Generally, last year's participants used a pipelined approach to build
%summaries, generally ranking sentences, filtering out all but the most
%relevant, and then performing some sort of deduplication/redundancy removal
%step.  Ranking approaches ranged from simple query word match to more
%sophisticated query expansion and query based language model scoring
%\cite{liu2013ictnet,xu2013trec,baruah2013univ}.  Perhaps most similar to our
%approach, the system of \cite{xu2013trec} uses a weighted combination of
%features (similarity to query, named entity frequency, predicate frequency,
%presence of numerical values, sentence novelty, etc.) to score sentences;
%sentences above a threshold are added to the summary.  Both the weights and
%the threshold are selected by hand.
%
%
%Our system seeks to combine the best of these approaches, using supervised
%learning to predict salience rankings, and directly incorporate this
%information in a clustering algorithm to bias the formation of sentence
%clusters around highly salient regions.

%Broadly, we conceive of the above

%Another popular graph-based model

%Larger clusters generally indicate more important For example

%\cite{} also explore the use of a hidden Markov model to predict summary
%inclusion based on previously selected sentences.

%ranking.
%
%The field of extractive summarization has long been focused on determing
%sentence importance or salience.  Many These efforts have largely involved
%unsupervised, data-driven approaches, where systems rank input sentences
%using features easily computable from the input, and sometimes an unrelated
%background corpus.  The most basic sentence rankings are by average word
%probability and average TF-IDF score, statistics that are computable from the
%input alone.  One of the more effective techniques, topic-sigantures,
%involves identifying the most topically related words in the input sentences.
%This is done using a log-likelihood ratio test ($\chi^2$) to determine which
%of two hypotheses hold for a word in the input: (1) the probability of the
%word in the input distribution and the background distribution are identical,
%or (2) the probability of the word is greater in the input distribution than
%in the background distribution. If (2) is true with some statistical
%significance, the word is said to be a topic signature. As with the previous
%features, a common approach is to rank sentences by the number of
%topic-signatures they contain.
%
%In mulit-document summarization, clustering algorthims are often employed to
%determine sentence importance, with larger clusters corresponding to more
%important topics. 
%
%Supervised learning approaches have also been explored. Features are usually
%derived from human generated summaries, and are non-lexical in nature (e.g.,
%sentence starting position, number of topic-signatures, number of unique
%words, word frequencies). Seminal work in this area has employed naive Bayes
%and logistic regression classifiers to identify sentences for summary
%inclusion. \cite{} also explore the use of a hidden Markov model to predict
%summary inclusion based on previously selected sentences.
%
%If this  
%
%tried to rank sentences by their overlap with query words. 
%

%and models are developed to predict the likelihood of a sentences inclusion
%in a summary. Naive Bayes, hidden Markov models, and logistic regression to
%predict a sentence's summary inclusion.
%
%Researches have also experimented with supervised learning for summarization,
%however, machine learning approaches have not yielded significant advances in
%generic summarization. One difficulty is that gold data is difficult to
%obtain.
%
%
%In  
%
%
%%which remain competetive to supervised machine-learning techniques.
%
%have ranked sentences by
%
%
%their average word probability, average TF-IDF weighting, and/or topic
%signatures; these representations are all easily computable from the input
%sentences, and, for topic signatures, an unrelated background corpus.  Topic
%signatures in
%
% 
%These efforts can be broadly split into two camps: feature based ranking and
%clustering.
%
%
%
%Determing sentence importance has been A large portion of automatic
%summarization research has focused on  
%
%

%\newcommand{corpus}{}

%A common approach to automatic summarization is to identify sentences with the
%highest centrality with respect to the input sentences.  Intuitively,
%sentences with a high degree of centrality are more semantically related to
%the entire set of input sentences.  A summary can thus be obtained by
%returning the $k$ most central sentences.  This generally implies the
%calculation of pairwise distances between all sentences
%\cite{radev2004centroid, erkan2004lexrank}.  In these approaches, sentences
%are evaluated extrinsically by their distance to other sentences, either
%directly \cite{erkan2004lexrank} or through an aggregate centroid object
%\cite{radev2004centroid}. The distance between sentences is most commonly the
%cosine distance of sentence term-vectors, but in general this can be an
%arbitrary real-valued similarity function.
%%; the distance function imposes a topology on the space of input sentences.
%
%For some domains, it is very likely that we will have additional background
%knowledge that could be predictive of sentence salience for the event being
%summarized.  For example, certain kinds of information extracted from the
%sentence text (e.g., temporal or geographic proximity) can indicate relevance
%to a given event.  It would be difficult to incorporate this kind of salience
%into the measure of centrality.
%
%
%For example, consider a cluster of three sentence vectors $s_1 = (1,1,0)$,
%$s_2 = (1,1,1)$, and $s_3 = (0,1,1)$. Without any other information, $s_2$ has
%the highest degree of centrality, i.e. it has the highest average cosine
%similarity and smallest average Euclidean distance to the other sentences.
%Now, if we believe that $s_1$ is $\alpha$ times more salient than the other
%sentences, we cannot simply scale $s_1$ by $\alpha$--the average cosine
%similarity will remain unchanged, since the vector magnitude does not affect
%the angle and $s_1$ will have an even greater the average Euclidean distance
%from the rest.  Worse still, $s_2$ will still be the most representative
%sentence of the three.
%
%

%In order to predict the salience score for a sentence,

 %\cite{guo2012simple} produces a real-valued score of the similarity We use
 %\cite{guo2012simple} produces real valued similarity scores s.
 %\cite{guo2012simple} determines the similarity of two sentences by deriving
 %low dimensional We have As a proxy measure for sentence salience, we use the
 %maximum similarity of an input sentence to a human generated summary
 %sentence, using the state-of-the-art sentence similarity module of
 %\cite{guo2012simple}. \cite{guo2012simple} derive a lower-dimensional vector
 %of latent features for a sentence. The similarity of two sentences is then
 %the cosine similarity of the latent vectors.  In order to predict this
 %similarity we extract a variety of features including language model scores,
 %geographic relevance, and temporal relevance.  We learn a predictive
 %function of sentence-summary similarity by fitting a Gaussian process model
 %on these features. \cite{preotiuc2013temporal}

%As training data for this model, we take a portion of the sentences found in
%the relevant documents and find their highest similarity to the gold nugget
%information seen thus far.

%When assigning preference scores

%After obtaining similarity scores for sentences in our training set, we fit a
%Gaussian process model to learn

%Our model

%Correllating automatic measures of sentence salience with human judgments is
%a difficult task. , we use the maximum cosine similarity to

%For example, if we scaled the BOW vector based on our belief in its salience,
%it would not effect the cosine distance since the angle between two vectors
%is not changed by the magnitude of either

%Simply scaling the sentence vector based on our belief in it's fitness does
%not with our prior beliefs-- When using the BOWs representation, the input
%space is lexically defined, but our salience metric may not be based on any
%specific lexical items.

%These approaches make it difficult to leverage prior knowledge to guide the
%selection of salient sentences. Sentences

%
%Centroid based algorthims are commonly employed in the summarization
%literature to compress a large number of sentences into a much smaller,
%representative set. 
%
%The $k$-medoids clustering algorithm is commonly used to partition input
%sentences into topically distinct clusters, where the most representative
%sentences (the cluster medoids) are taken to build the summary. The quality
%of the summary in this framework is dependent on the method of sentence
%representation and the ability of a similarity or distance metric to
%adequately capture pairwise comparisons between sentences. Previous work in
%event clustering has examined the use of different term weightings (tf-idf,
%named-entities)  and lower dimensional term representations (LSA, LDA) for
%use in summarization.
%
%
%A popular graph-based alternative, LexRank, treats each sentence as a node in
%a graph, and identifies the nodes that are most central by in-degree.  The
%existence of an edge between two sentences is determined by a similarity
%function (either by setting a threshold above which the edge exists, or by
%taking the similarity as a continuous edge weight). The sentences with the
%highest eigenvector centrality can be found using random walks (PageRank).
%The $k$ most central sentences are used as the summary.
%
%One drawback of these algorithms is that they do not provide an elegant way
%to incorporate prior information about sentence salience.

%Move this out!
%In our approach, the system generates clusters using an affinity propagation
%algorithm and from each cluster an exemplar sentence is selected that is added
%to the summary.  In the following sections, we show how  prior information
%representing salience can easily be incorporated into the affinity propagation
%algorithm.  We believe the incorporation of salience to be useful in noisy
%environments (e.g., a web crawl), and that it can help the formation of
%clusters around the most relevant inputs. Our current system  is trained using
%features derived from location, changes in wording across time and language
%models that characterize the language of disaster to generate summaries at
%regular intervals across time.  As we develop the system further, we will
%extend it to generate updates across time,  penalizing the salience of
%concepts already selected by the summarizer to encourage the discovery of
%novel sentences as the event unfolds. 
%

%\begin{table*}[ht] \begin{center} \begin{tabular}{| c p{7.0cm} || c p{7.0cm}
%|} \hline Preference & AP Clustering & Preference & $k$-Medoids Clustering\\
%\hline 9.010 & The magnitude-7.5 quake, about 20 miles deep, was centered off
%the town of Champerico .People fled buildings in Guatemala City , in Mexico
%City and in the capital of the Mexican state of Chiapas , across the border
%from Guatemala & 9.010 & The magnitude-7.5 quake, about 20 miles deep, was
%centered off the town of Champerico .People fled buildings in Guatemala City ,
%in Mexico City and in the capital of the Mexican state of Chiapas , across the
%border from Guatemala   \\ \hline 9.010 & A reporter in the town of San Marcos
%, about 80 miles north of the epicenter, told local radio station Emisoras
%Unidas that houses had collapsed onto residents and smashed televisions and
%other appliances had been scattered into the streets.  & 3.007 & ``Things fell
%in my kitchen .'' Perez said more than 2,000 soldiers were deployed from a
%base in San Marcos to help with disaster relief.\\ \hline 9.007 & The local
%fire department said on its Twitter account that a school had collapsed and
%eight injured people had been taken to a nearby hospital.  & 3.007 &  Ingrid
%Lopez , who went to the hospital with a 72-year-old aunt whose legs was
%crushed by a falling wall, said she had waited hours for an X-ray.\\ \hline
%7.008 & There are three confirmed dead and many missing after the strongest
%earthquake to hit Guatemala since a deadly 1976 quake that killed 23,000.  &
%1.007 & Hundreds of people crammed into the hallways of the small town
%hospital waiting for medical staff to help out hundreds of injured family
%members, some complaining they were not getting care quickly enough. \\ \hline
%\end{tabular} \end{center} \caption{Example summary using affinity propagation
%(left) and $k$-medoids (right)} \end{table*} \begin{table*}[t] \begin{center}
%\begin{tabular}{| c || c | c | c || c | c | c || c | c | c |} \hline Method &
%\multicolumn{3}{c}{ROUGE-1} & \multicolumn{3}{c}{ROUGE-2} &
%\multicolumn{3}{c}{ROUGE-3} \\ & Recall & Prec. & F-1 & Recall & Prec. & F-1 &
%Recall & Prec. & F-1 \\ \hline $k$-medoids & 0.127 & 0.414 & 0.181 & 0.025 &
%0.076 & 0.035 & 0.003 & 0.010 & 0.005\\ \hline AP & 0.117 & 0.440 & 0.173 &
%0.022 & 0.082 & 0.033 & 0.004 & 0.015 & 0.006\\ \hline \end{tabular}
%\end{center} \caption{ROUGE scores for $k$-medoids and affinity propagation
%methods} \end{table*}
%
%
%
%
%\section{Experiments}
%
%We carried out a small set of initial experiments on one event.  We collected
%a subset of pages from the TREC Stream Corpus that were relevant to a 2012
%earthquake off the coast of Guatemala, and further subdivided this collection
%by the hour they were created. For each hour we generated a summary using the
%AP clustering algorithm. 
%
% We also generated baseline summaries using the $k$-medoids (using the
% Partitioning Around Medoids algorithm), setting $k = |\mathcal{E}|$ , i.e.
% the number of exemplar sentences returned by the AP. Because $k$-medoids
% begins with a random initialization, we took the best (minimum average
% distance) result of 100 restarts.
%
%Table 1 shows example output of the AP and $k$-medoids generated summaries.
%Sentences are ranked by preference score, although preference has no effect on
%the $k$-medoids algorithm.  Quantitatively, AP exemplar sentences had higher
%predicted sentence quality scores (preferences) than the cluster medoids.
%Qualitatively, the AP method appears to select more general details about the
%earthquake. Looking at the third sentence selection in table 1, we can see
%that $k$-medoids selects a personal experience that was reported. This is
%perhaps less newsworthy or reportable compared to the third sentence in in the
%AP generated summary which reports a notable structure collapse and injuries
%related to the quake.  We believe AP results in a more readable and
%informative summary, although we have yet to perform a rigorous human
%evaluation of the summary output.
%
%
%We evaluated both algorithms with the ROUGE toolkit \cite{lin2004rouge}.
%N-ROUGE works by calculating the n-gram recall and precision of an
%automatically generated summary in reference to a model summary.  We created
%model summaries by taking the gold nugget sentences with timestamps up to and
%including the current system time as the gold summary for that hour.
%%\fdcomment{may be interesting to measure track metrics to measure latency,
%%redundancy, etc.} KM - Ask Chris
%
%Table 2 shows average recall, precision, and F-measure for various orders of
%ROUGE score. AP demonstrated consistently higher precision than our baseline.
%%scores over $k$-medoids (ROUGE evaluations are usually focused on recall).
%While not statistically significant, it is difficult to show significance with
%Rouge using a small test; we hope further tests will confirm this improvement. 
%%   , AP had higher precision on average.
%On average, the AP summaries were slightly shorter than the baseline, which
%would partially explain this difference. It is also possible that our language
%models are biased toward shorter sentences; we are more likely to have seen a
%shorter sentence in the language model input.
%%\fdcomment{is there a theory to why this is happening?}
%We are currently adapting our summarizer to add updates over time, and
%maintaining precision will be important to prevent topic drift.  
%
%
%
%%\begin{table}[h!] \tiny \begin{center} \begin{tabular}{| c p{3.5cm} |} \hline
%%Preference & Sentence\\ \hline 9.010 & The magnitude-7.5 quake, about 20
%%miles deep, was centered off the town of Champerico .People fled buildings in
%%Guatemala City , in Mexico City and in the capital of the Mexican state of
%%Chiapas , across the border from Guatemala\\ \hline 3.007 & "Things fell in
%%my kitchen ." Perez said more than 2,000 soldiers were deployed from a base
%%in San Marcos to help with disaster relief.\\ \hline 3.007 & Ingrid Lopez ,
%%who went to the hospital with a 72-year-old aunt whose legs was crushed by a
%%falling wall, said she had waited hours for an X-ray. \\ \hline 1.007 &
%%Hundreds of people crammed into the hallways of the small town hospital
%%waiting for medical staff to help out hundreds of injured family members,
%%some complaining they were not getting care quickly enough. \\ \hline
%%\end{tabular} \end{center} %  \caption{Example summary using $k$-medoids with
%%100 random restarts} \end{table}
%
%
%

%\section{Conclusions and Future Work}

%We have developed a summarizer that can generate summaries over time from web
%crawls on disasters. We show that our method of identifying exemplar sentences
%for a summary using AP clustering produces  summaries with higher precision
%    compared to those based on clustering with K-medoids. A key component of
%    our approach is the prediction of salient information using features based
%    on location, temporal changes in topic, and two different language models.
%
%Currently, we run each hour of summarization independently. In order to avoid
%repeating information, we would like to incorporate previously chosen
%exemplars in the preference computation. One possibility would be to
%down-weight a candidate exemplar's preference based on its similarity to
%previous exemplars.
%
%Secondly, we would like to do more intelligent inference of missing
%geographical information since not all sentences contain locations. Currently
%we are using mean values for missing data.
%
%Finally, we would like to experiment with non-symmetric similarity matrices,
%specifically using narrative chains\cite{chambers2009unsupervised}. Under this
%model $S(i,j)$ would express the likelihood that the events in sentence $j$
%precede the events in sentence $i$. We hope such a parameterization would
%promote more causally motivated sentences into exemplar positions, which would
%better describe the disaster event domain.
%
%
\bibliographystyle{abbrv}
%\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this
%case
\bibliography{cites.bib}
% You must have a proper ".bib" file and remember to run: latex bibtex latex
% latex to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional \balancecolumns \balancecolumns % GM June 2007 That's
%all folks!
\end{document}

>>>>

\documentclass{sig-alternate} 
\usepackage{url} 
\usepackage{color}
% \documentclass[10pt]{article} \usepackage{url} \usepackage{color}
\usepackage[utf8]{inputenc}
% \usepackage[margin=1in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[]{algorithm2e}
\DeclareMathOperator{\corpus}{\mathcal{C}}
\DeclareMathOperator{\doc}{\mathnormal{d}}
\DeclareMathOperator{\sent}{\mathnormal{s}}
\DeclareMathOperator{\order}{\pi}
\DeclareMathOperator{\dtime}{\mathnormal{t}}
\DeclareMathOperator{\hour}{\mathnormal{h}}
\DeclareMathOperator{\hours}{\mathcal{H}}
\DeclareMathOperator{\Sim}{\mathbf{K}}
\DeclareMathOperator{\SMat}{\mathbf{X}}
\DeclareMathOperator{\Pref}{\boldsymbol{\pi}}
\DeclareMathOperator{\Exemp}{\mathnormal{Exemplars}}
\DeclareMathOperator{\Updates}{\mathnormal{Updates}}
\usepackage{cleveref}
\crefname{section}{§}{§§}
\Crefname{section}{§}{§§}

@@

\title{The Anatomy of a Temporal Summarization System}

\numberofauthors{1} %  in this sample file, there are a *total*
\author{}
% \author[1]{Chris Kedzie}
% \author[1]{Kathleen McKeown}
% \author[2]{Fernando Diaz}
% \affil[1]{Columbia University, Department of Computer Science}
% \affil[2]{Microsoft Research}
%    Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
%Format\titlenote{(Produces the permission block, and copyright information).
%For use with SIG-ALTERNATE.CLS. Supported by ACM.}} \subtitle{[Extended
%Abstract] \titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement and
% alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time' i.e. three
% 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of "name/affiliations" may
% appear. We just ask that you restrict the number of 'columns' to three.
%
% Because of the available 'opening page real-estate' we ask you to refrain
% from putting more than six authors (two rows with three columns) beneath the
% article title.  More than six makes the first-page appear very cluttered
% indeed.
%
% Use the \alignauthor commands to handle the names and affiliations for an
% 'aesthetic maximum' of six authors.  Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the \additionalauthors
% command.  These 'additional authors' will be output/set for you without
% further effort on your part as the last section in the body of your article
% BEFORE References or any Appendices.

@@

\input{introduction.tex}

\input{relatedwork.tex}

@@

\begin{figure*}
	\begin{center}
\begin{tabular}{| p{5cm} c c |}
\hline
Event & WP Categories & No. Docs/Sents/Words\\
\hline \hline
Boston\_Marathon\_bombings \newline
Christopher\_Dorner\_shootings\_and\_manhunt \newline 
 In\_Amenas\_hostage\_crisis
& Terrorism, Mass Shootings & 33,732/1,139,588/26,201,659  \\
\hline
 Cyclone\_Oswald \newline
Early\_2012\_European\_cold\_wave \newline
February\_2013\_noreaster \newline & Weather events & 35,554/591,850/12,794,438  \\
\hline
Costa\_Concordia\_disaster & Accidents & 22,874/732,945/16,520,242 \\
\hline
Chelyabinsk\_meteor & Earthquakes & 14,515/283,509/6,135,803  \\
\hline
Port\_Said\_Stadium\_riot \newline
2012\_Afghanistan\_Quran\_burning\_protests \newline
2011-13\_Russian\_protests \newline
2012\_Romanian\_protests \newline
2012-13\_Egyptian\_protests \newline
2013\_Bulgarian\_protests\_against\_the\_Borisov\_cabinet \newline
2013\_Shahbag\_protests & Activism\_by\_type & 464,657/11,254,122/250,172,896  \\
\hline
\end{tabular}
\caption{Domain specific Wikipedia corpora for semantic similarity and 
language models. }
\end{center}
\end{figure*}

@@

% \begin{figure}
% \centering
\begin{algorithm}%[H]
 \KwData{$Query$ --- the set of event query words\\ 
        $SC$ --- the stream corpus\\

@@

 } 
 \caption{Temporal Summarization Algorithm}
\end{algorithm}
% \end{figure}

@@

\bibliographystyle{abbrv}
%\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this
%case
\bibliography{cites.bib}
% You must have a proper ".bib" file and remember to run: latex bibtex latex
% latex to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional \balancecolumns \balancecolumns % GM June 2007 That's
%all folks!
\end{document}
